Title

### 2023-05-09 main.tex
hacky sack

% Bold the 'Figure #' in the caption and separate it from the title/caption with a period
% Captions will be left justified
\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}
\renewcommand{\figurename}{Fig}

% Use the PLoS provided BiBTeX style
\bibliographystyle{plos2015}

@@

% }}}
% }}}
\section{Circuit for a Pauli Channel} % {{{
\label{sec: Circuit for a Pauli Channel}
\cpnote{Acá voy}

In this section we propose a quantum circuit that simulates $N$-qubit Pauli
channels.  Moreover, we implement the circuit for $N=1$ on a quantum computer
and analyze the results using the diamond norm.
\cpnote{Quizá en una frase poner el resultado aca o ampliar
tantito} \tbnote{Va, agregué lo siguiente: 
We conclude that the circuit performs optimally for channels  in proximity to the
completely depolarizing channel but
it is deficient close to unitary channels.}

\subsection{Description of the Circuit for a Pauli Channel} %{{{
\label{subsec: Description of the circuit}

\cpnote{Yo abriría este parrafo con una frase que de la idea muy general. Decir 
algo asi como que vamos a crear un estado conque contenga a las $k$s 
como coeficientes y leugo controlar la aplicación de los Pauli strings. Luego
ya dar los detalles. Así incluso mas escueto de lo que pongo. Por ejemplo:
To design the circiot that implements 13, we construct a state that incorportes
probabilities $k$ and subsequently apply controlled operation. In particular... }
\cpnote{No me gusta como está organizado este parrafo. Le puedes dar una iterada?}
\tbnote{Propongo el párrafo en naranja para sustituirlo}

To design the circuit, we remember that a Pauli channel as the one in
eq.~(\ref{eq: pauli channel N-qubit})
applies each Pauli operator $\sigma_{\vec{\gamma}}$ on $\rho$ with a probability $k_{\vec{\gamma}}$.
Given this, it is easy to construct a quantum circuit that implements 
a Pauli channel with the help of $2N$ ancilla qubits,
the circuit that does this is presented in fig. (\ref{fig: circuit-pauli}).
The general idea is to produce the probabilities $k_{\gamma}$ by creating the state
\begin{eqnarray}
\label{eq: state0}
\sum_{\vec{\gamma}} b_{\vec{\gamma}} |\vec{\gamma} \rangle
\end{eqnarray}
in the ancilla qubits, 
where $b_{\vec{\gamma}}$ are numbers such that $
|b_{\vec{\gamma}}|^2 = k_{\vec{\gamma}}$.
The $2N$-qubit state $|\vec{\gamma}\rangle$  is defined by $|\gamma_1 \rangle \cdots |\gamma_N\rangle$.

{\color{orange} Cambiar por:  To design the circuit that implements \ref{eq: pauli channel N-qubit}, we construct a state that incorportes
probabilities $k_{\gamma}$ on ancilla qubits and subsequently apply controlled 
Pauli operations on the principal qubits.
The circuit that does this is presented in fig. (\ref{fig: circuit-pauli})
and works by creating the state
\begin{eqnarray}
\label{eq: state}
\sum_{\vec{\gamma}} b_{\vec{\gamma}} |\vec{\gamma} \rangle
\end{eqnarray}
on the ancilla qubits, where $b_{\vec{\gamma}}$ are numbers such that $
|b_{\vec{\gamma}}|^2 = k_{\vec{\gamma}}$ and
the $2N$-qubit state $|\vec{\gamma}\rangle$ is defined by $|\gamma_1\rangle \cdots |\gamma_N\rangle$.
}

%Moreover $|\vec{\gamma}\rangle$ is defined as a $2n$ qubit state given by
%\begin{eqnarray}
%|\vec{\gamma} \rangle = |\gamma_1\rangle |\gamma_2 \rangle \cdots |\gamma_N \rangle,
%\end{eqnarray}
%where $|\gamma_i \rangle$ is the $2$ qubit state $|00\rangle, |01\rangle , |10\rangle$ or $|11\rangle$ when $\gamma_i = 0,1,2,3$ respectively. \\

\begin{figure}[h!]
\centering
% \begin{quantikz}
% \lstick{$q:\; |0\rangle^{\otimes N}$} & \qw & \gate{\sigma_{\vec{\gamma} }} \gategroup[wires=2,steps
% =1,style={dashed, inner sep=4pt}]{Repeat for all $\vec{\gamma}$}
% \gategroup[wires=2,steps
% =1,style={dashed, inner sep=4pt}, label style = {label position = below, yshift = 0.15cm}]
% {$|\vec{\gamma}\rangle$} & \qw \\
% \lstick{$\tilde{q}:\; |0\rangle^{\otimes 2N}$} & \gate[wires=1]{\text{Create the $2N$ qubits state $\sum_{\vec{\gamma}} b_{\vec{\gamma}}   |\vec{\gamma} \rangle$}} & \ctrl{-1} 
% % \gategroup[wires=1,steps
% %=1,style={color=white, inner sep=0pt}, label style= {label position=below}]{$|\vec{\gamma}\rangle$} 
% & \qw 
% \end{quantikz}
\includegraphics{images/circuito_general.pdf}
\caption{\cpnote{Revisa el archivo images/circuito\_general.pdf y el makefile correspondiente} \tbnote{Oh, ya veo, gracias!.} {\bf Circuit for an $N$-qubit Pauli channel on $N$ qubits.}
The circuit creates the state $\sum_{\vec{\gamma}} b_{\vec{\gamma}}|\vec{\gamma}\rangle$ 
on the $2N$ ancilla qubits denoted by $\tilde{q}$. }
\label{fig: circuit-pauli}
\end{figure}

\cpnote{La primera frase es cierta, pero no le veo el sentido acá. Trata de reformular el parrafo 
de nuevo. Croe que el ``This means'' definitivamente no va y es el que le da un sentido ``raro''. 
Itera (quizá solo quitando esas dos palabras)} \tbnote{Concuerdo, quité eso.}
When measured in the computational basis, the state given in eq.~(\ref{eq: state})
collapses to $|\vec{\gamma}\rangle$ with a 
probability $|b_{\vec{\gamma}}|^2 = k_{\vec\gamma}$. 
The circuit in fig.~(\ref{fig: circuit-pauli}) uses this fact
to operate $\sigma_{\vec{\gamma}}$ on the principal qubits
with a probability $k_{\vec\gamma}$ by using controlled operations 
that apply $\sigma_{\vec{\gamma}}$ to the principal qubits
only if the ancilla qubits are in the state $|\vec{\gamma}\rangle$.
Therefore, the circuit from fig.~(\ref{fig: circuit-pauli}) 
applies each operation $\sigma_{\vec{\gamma}}$ to the principal qubits 
with a probability $k_{\vec{\gamma}}$, 
just as a Pauli channel is supposed to do.  
\cpnote{Del circuito, parece ue las fases de las bs gammas no omportan mucho (o nada). 
Esa libertad la hemos considerado? De alguna manera colapsan curvas de las que
hemos visto?} \tbnote{Sí, es una libertad que se tiene y he considerado y significa que hay muchas elecciones de $b_{\gamma}$ para un mismo canal.
Es una de las varias cosas que complicaba determinar uno a uno qué canales se pueden hacer.}

%}}}
\subsection{Simulation for one-qubit Pauli channels} % {{{
\label{subsec: Simulation for one-qubit Pauli channels}
\cpnote{Es raro tener una sola subseccion. De perdida dos, o ninguna. Charlemso a ver como 
reorganizar las secciones (creo que el flujo si va bien hasta ahora)} \tbnote{Va. Me pareció ponerle su propia subsección a la parte anterior porque creo que esto y lo anterior sí debe ir separado, así que mejor dos subsecciones.}

For the particular case of a Pauli channel on one qubit, the circuit that
simulates it can be constructed as in fig.~\ref{fig: circuit-pauli-1},
 which is a special case of fig. \ref{fig: circuit-pauli}
 but with all details \cpnote{y compuertas , etc digamos que details}\tbnote{Va, listo} explicitly shown.

\begin{figure}[h!]
\centering
\includegraphics{images/circuito_unqubit.pdf}
\caption{\cpnote{si quieres, intenta hacer la figura tu solo basado en el lo quehabía hecho.} \tbnote{Va, lo hice así, espero haberlo hecho bien.} \cpnote{ 
Otra cosa quizá para discutir.  La creacion del estado especial de dos qubits no esta
aca explicita. Eso creo que si lo podemos hacer en general, o no? Como sería eso? Lo discutimos
a ver si lo pones?} \tbnote{Sí. En la figura que está ahora lo puse (antes sólo había un bloque que
 decía que se crea el estado $|b\rangle$ sobre los qubits de ancilla).
Ahora que lo pienso, sí lo prefiero así con la creación explícita y creo que mejora a la discusión después,
porque muestra que en general se necesitan tres ángulos y es lo que luego buscamos 
reducir a sólo uno}
 {\bf One qubit Pauli channel circuit.} Circuit for a one-qubit Pauli channel, which is a particular case of Fig~(\ref{fig: circuit-pauli}).
Here we have two ancilla qubits, and the state 
$b_{00} |00\rangle + b_{01} |01\rangle + b_{10} |10\rangle + b_{11}|11\rangle$ 
is created on them with the help of three rotations of angles $\theta_0 = \arg(\sqrt{k_{00}} + i \sqrt{k_{01}}) - \arg(\sqrt{k_{10}} + i\sqrt{k_{11}})$, 
$ \theta_1 = 2 \arccos(\sqrt{k_{00} + k_{01}})$ and
$ \theta_2 = \arg(\sqrt{k_{00}} + i \sqrt{k_{01}}) + \arg(\sqrt{k_{10}} + i\sqrt{k_{11}})$. }
\label{fig: circuit-pauli-1} 
\end{figure}
Taking advantage of the quantum computers that IBM has available~\cite{Qiskit},
we sampled $249$ one-qubit Pauli channels and simulated them using the 
ibmq-lima quantum computer. 
For each of these channels, we used quantum process tomography~\cite{Qiskit,
Chuang:1996} to obtain the {\color{red} Choi matrix} {\color{orange} operator $\xi_I$}  corresponding to the implementation of
the circuit {\color{red} $\mathcal{C}_{I}$} .
Then, we compared this {\color{red} Choi matrix} {\color{orange} operator} with the theoretical
{\color{red} Choi matrix $\mathcal{C}_T$} {\color{orange} operator $\xi_T$} 
of the channel we wanted to implement.
\cpnote{Quizá referirnos mejor al canal? Lo discutimos.} 
\tbnote{Ah sí, mejor. Cambié lo que puse en rojo por lo que está en naranja.}

To perform this comparison, we used the diamond norm~\cite{Aharonov,Wilde},
which gives us a method of discriminating \cpnote{creo qeu todas lasnormas nos
permiten discriminar entre canales. itera} \tbnote{Lo cambié un poco para que no se entienda que diamond es la única que lo hace} between quantum channels.
Suppose an agent is given one of the channels $\xi_I$, $\xi_T$
with probability $1/2$ for each \cpnote{que pasa para una probabilidad $p$?}
\tbnote{Hay una expresión similar pero que depende de $p$. Lo pongo con $p$ en general?} 
\cpnote{Otra cosa, los canales no se caracterizan por lo general po rla matriz 
de choi, tonces por aca quizá hay problemas. Discutamos notacion.} \tbnote{Sip, lo cambié},
and tries to guess which channel they received
by passing through it a state $\rho$ and measuring the result.
Then, the maximal probability of success (out of all possible states $\rho$) that
the agent guesses correctly is~\cite{Benenti}:
\begin{equation}
\label{eq: probability-success}
p_{succ} = \dfrac{1}{2}+ \dfrac{1}{4} ||\xi_I - \xi_T ||_{\diamond},
\end{equation}
where $|| \cdot ||_{\diamond}$ is the diamond norm.  Notice that $p_{succ}=1/2$
means that the channels are the same \cpnote{qioza una frase explicando porque
esto es razonable}
\tbnote{Cambiar la oración pasada por:} {\color{orange} Notice that if the channels are the same, then $p_{succ}=1/2$. 
This is expected because in this situation the agent
has no way of distinguishing the channels and has no choice but to completely
guess, which results in a probability of success of $1/2$.}
On the other hand, $p_{succ}=1$ indicates that the channels are perfectly
distinguishable \cpnote{hummm ejemplo al menos para nosotros.} 
\tbnote{Un ejemplo que comprobé es considerar el canal que aplica $\sigma_x$ y 
el que aplica $\sigma_z$ y tienen $p_{succ}=1$.
De hecho, al tomar dos canales que consistan en aplicar $\sigma_i$ y $\sigma_j$ 
(para $i\neq j$), se cumple esto.
También quería ejemplos no unitarios, pero no encontré.}

Finally, using the representation of Pauli channels in a tetrahedron as
in eq.~(\ref{eq: conditions-tetrahedron}),
we show in fig.~(\ref{fig: fidelity one qubit}) the maximal probabilities of
success defined by eq. (\ref{eq: probability-success}) for the channels
analyzed. \cpnote{Falta analisis de los resultados. } 
\tbnote{Agregar: } {\color{orange} We can see that channels close to the 
completely depolarizing
channel (that is close to the center of the tetrahedron)
have a low $p_{succ}$, while those 
close to unitary channels have much higher $p_{succ}$.
This means that channels closer to the 
completely depolarizing channel are simulated better on the quantum computers.
This is reasonable because quantum computers are prone to errors
that depolarize qubits, which isn't very problematic
when trying to simulate depolarization but it is 
when simulating unitary processes.}

\cpnote{Mejorar la figura, quizá dejando la tridimensional y ademas poniendo unos 6 cortes. Probar
con diferentes colores.
}

\begin{figure}[h!]
\centering
\includegraphics[width=0.45\textwidth]{probabilities-points.png}\\
\caption{\tbnote{Al igual que antes, hay que quitar esta figura y ponerla en un archivo a parte}. {\bf Maximal probabilities of success for one-qubit Pauli channel} $p_{succ}$ of one-qubit Pauli channels implemented on IBM's ibmq-lima. The channels are plotted in the tetrahedron of Pauli channels, with a color bar indicating the distinguishability of each channel's implementation using the circuit for a 1-qubit Pauli channel.}
\label{fig: fidelity one qubit}
\end{figure}

@@

\newpage

@@

%\textbf{Puntos:}
%\begin{itemize}
%\item Use the last theorem to conclude directly which maps can be created using an OPR circuit.
%\item \textbf{Examples:} Show examples that satisfy these conditions: Bit-Flip, parabolic maps, etc. 
%and an example that doesn't satisfy the conditions (ejemplo está en la tesis).
%\end{itemize}
% }}}

\newpage
\section{Exponential maps $e^{iHt}$} % {{{
\label{sec: Exponential maps}
\textbf{Puntos:}

>>>>

% Bold the 'Figure #' in the caption and separate it from the title/caption with a period
% Captions will be left justified
\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}
\renewcommand{\figurename}{Fig}
\renewcommand{\succ}{\textrm{succ}}

\newcommand{\fref}[1]{Fig.~\ref{#1}}
\newcommand{\eref}[1]{eq.~(\ref{#1})}
% Use the PLoS provided BiBTeX style
\bibliographystyle{plos2015}

@@

% }}}
% }}}
\section{Circuit for a Pauli Channel} % {{{
\label{sec: Circuit for a Pauli Channel}
% Intro {{{

In this section we propose a quantum circuit that simulates $N$-qubit Pauli
channels.  Moreover, we implement the circuit for $N=1$ on a quantum computer
and analyze the results using the diamond norm.
We find that close to the depolarizing channel, the general circuit simulator 
can implement such channels with the highest fidelity. 
% produce the highest 
% \cpnote{Quizá en una frase poner el resultado aca o ampliar
% tantito} \tbnote{Va, agregué lo siguiente: 
% We conclude that the circuit performs optimally for channels  in proximity to the
% completely depolarizing channel but
% it is deficient close to unitary channels.}
% }}} 
\subsection{Description of the Circuit for a Pauli Channel} %{{{
\label{subsec: Description of the circuit}

% \cpnote{Yo abriría este parrafo con una frase que de la idea muy general. Decir 
% algo asi como que vamos a crear un estado conque contenga a las $k$s 
% como coeficientes y leugo controlar la aplicación de los Pauli strings. Luego
% ya dar los detalles. Así incluso mas escueto de lo que pongo. Por ejemplo:
% To design the circiot that implements 13, we construct a state that incorportes
% probabilities $k$ and subsequently apply controlled operation. In particular... }
% \cpnote{No me gusta como está organizado este parrafo. Le puedes dar una iterada?}
% \tbnote{Propongo el párrafo en naranja para sustituirlo}

% To design the circuit, we recall that a Pauli channel, as the one in
% eq.~(\ref{eq: pauli channel N-qubit}), applies each Pauli operator
% $\sigma_{\vec{\gamma}}$ on $\rho$ with a probability $k_{\vec{\gamma}}$.
% Given this, it is easy to construct a quantum circuit that implements 
% a Pauli channel with the help of $2N$ ancilla qubits,
% see \fref{fig: circuit-pauli}.
% The general idea is to produce the probabilities $k_{\gamma}$ by creating the state
% \begin{eqnarray}
% \label{eq: state0}
% \sum_{\vec{\gamma}} b_{\vec{\gamma}} |\vec{\gamma} \rangle
% \end{eqnarray}
% in the ancilla qubits, 
% where $b_{\vec{\gamma}}$ are numbers such that $
% |b_{\vec{\gamma}}|^2 = k_{\vec{\gamma}}$.
% The $2N$-qubit state $|\vec{\gamma}\rangle$  is defined as $|\gamma_1 \rangle
% \cdots |\gamma_N\rangle$.

% {\color{orange} Cambiar por:  
To design the circuit that implements \eref{eq: pauli channel N-qubit}, we construct a state that 
includes the probabilities $k_{\gamma}$ on the ancilla qubits and subsequently
apply controlled Pauli operations on the main qubits.  The circuit that does
this is presented in \fref{fig: circuit-pauli}.

\begin{figure} % {{{
\centering
% \begin{quantikz}
% \lstick{$q:\; |0\rangle^{\otimes N}$} & \qw & \gate{\sigma_{\vec{\gamma} }} \gategroup[wires=2,steps
% =1,style={dashed, inner sep=4pt}]{Repeat for all $\vec{\gamma}$}
% \gategroup[wires=2,steps
% =1,style={dashed, inner sep=4pt}, label style = {label position = below, yshift = 0.15cm}]
% {$|\vec{\gamma}\rangle$} & \qw \\
% \lstick{$\tilde{q}:\; |0\rangle^{\otimes 2N}$} & \gate[wires=1]{\text{Create the $2N$ qubits state $\sum_{\vec{\gamma}} b_{\vec{\gamma}}   |\vec{\gamma} \rangle$}} & \ctrl{-1} 
% % \gategroup[wires=1,steps
% %=1,style={color=white, inner sep=0pt}, label style= {label position=below}]{$|\vec{\gamma}\rangle$} 
% & \qw 
% \end{quantikz}
\includegraphics{images/circuito_general.pdf}
\caption{{\bf Circuit for an $N$-qubit
Pauli channel on $N$ qubits.}
The circuit creates the state $\sum_{\vec{\gamma}} b_{\vec{\gamma}}|\vec{\gamma}\rangle$ 
on the $2N$ ancilla qubits denoted by $\tilde{q}$. }
\label{fig: circuit-pauli}
\end{figure} % }}}

The first part of the circuit involves the creation of the state
\begin{eqnarray}
\label{eq: state}
\sum_{\vec{\gamma}} b_{\vec{\gamma}} |\vec{\gamma} \rangle
\end{eqnarray}
on the ancilla qubits, where $b_{\vec{\gamma}}$ are numbers such that $
|b_{\vec{\gamma}}|^2 = k_{\vec{\gamma}}$ and
the $2N$-qubit state $|\vec{\gamma}\rangle$ is defined as $|\gamma_1\rangle
\cdots |\gamma_N\rangle$.
% \cpnote{La primera frase es cierta, pero no le veo el sentido acá. Trata de reformular el parrafo 
% de nuevo. Croe que el ``This means'' definitivamente no va y es el que le da un sentido ``raro''. 
% Itera (quizá solo quitando esas dos palabras)} \tbnote{Concuerdo, quité eso.}
When measured in the computational basis, the state given in eq.~(\ref{eq: state})
collapses to $|\vec{\gamma}\rangle$ with a 
probability $|b_{\vec{\gamma}}|^2 = k_{\vec\gamma}$. 
The circuit in fig.~(\ref{fig: circuit-pauli}) uses this fact
to apply $\sigma_{\vec{\gamma}}$ on the main qubits
with a probability $k_{\vec\gamma}$ by using controlled operations 
conditioned on the state of the system being $|\vec{\gamma}\rangle$,
just as the Pauli channel is supposed to do.  
% 
% that apply $\sigma_{\vec{\gamma}}$ to the main qubits
% only if the ancilla qubits are in the state $|\vec{\gamma}\rangle$.
% 
% Therefore, the circuit from fig.~(\ref{fig: circuit-pauli}) 
% applies each operation $\sigma_{\vec{\gamma}}$ to the principal qubits 
% with a probability $k_{\vec{\gamma}}$, 
% just as a Pauli channel is supposed to do.

\cpnote{Evaluar si al final ponemos algo al respecto de este comentario}
\cpnote{Del circuito, parece ue las fases de las bs gammas no omportan mucho (o nada). 
Esa libertad la hemos considerado? De alguna manera colapsan curvas de las que
hemos visto?} \tbnote{Sí, es una libertad que se tiene y he considerado y significa que hay muchas elecciones de $b_{\gamma}$ para un mismo canal.
Es una de las varias cosas que complicaba determinar uno a uno qué canales se pueden hacer.}

%}}}
\subsection{Simulation for one-qubit Pauli channels} % {{{
\label{subsec: Simulation for one-qubit Pauli channels}

\cpnote{Acá voy}

% \cpnote{Es raro tener una sola subseccion. De perdida dos, o ninguna. Charlemso
% a ver como reorganizar las secciones (creo que el flujo si va bien hasta
% ahora)} \tbnote{Va. Me pareció ponerle su propia subsección a la parte anterior
% porque creo que esto y lo anterior sí debe ir separado, así que mejor dos
% subsecciones.}

For the particular case of a Pauli channel on one qubit, the circuit that
simulates it can be constructed as in fig.~\ref{fig: circuit-pauli-1},
which is a special case of fig. \ref{fig: circuit-pauli}
but with all details  explicitly shown.

\begin{figure} % {{{
\centering
\includegraphics{images/circuito_unqubit.pdf}
\caption{
% \cpnote{si quieres, intenta hacer la figura tu solo basado en el lo quehabía hecho.} \tbnote{Va, lo hice así, espero haberlo hecho bien.} \cpnote{ 
% Otra cosa quizá para discutir.  La creacion del estado especial de dos qubits no esta
% aca explicita. Eso creo que si lo podemos hacer en general, o no? Como sería eso? Lo discutimos
% a ver si lo pones?} \tbnote{Sí. En la figura que está ahora lo puse (antes sólo había un bloque que
%  decía que se crea el estado $|b\rangle$ sobre los qubits de ancilla).
% Ahora que lo pienso, sí lo prefiero así con la creación explícita y creo que mejora a la discusión después,
% porque muestra que en general se necesitan tres ángulos y es lo que luego buscamos 
% reducir a sólo uno}
\cpnote{No me gusta que esté tan cargado de ecuaciones el caption. Metelas en
el lugar apropiado en el texto}
{\bf One qubit Pauli channel circuit.} Circuit for a one-qubit Pauli channel,
which is a particular case of Fig~(\ref{fig: circuit-pauli}).  Here we have two
ancilla qubits, and the state $b_{00} |00\rangle + b_{01} |01\rangle + b_{10}
|10\rangle + b_{11}|11\rangle$ is created on them with the help of three
rotations of angles $\theta_0 = \arg(\sqrt{k_{00}} + i \sqrt{k_{01}}) -
\arg(\sqrt{k_{10}} + i\sqrt{k_{11}})$, $ \theta_1 = 2 \arccos(\sqrt{k_{00} +
k_{01}})$ and $ \theta_2 = \arg(\sqrt{k_{00}} + i \sqrt{k_{01}}) +
\arg(\sqrt{k_{10}} + i\sqrt{k_{11}})$. }
\label{fig: circuit-pauli-1} 
\end{figure} % }}}

Using the quantum computers that IBM has available~\cite{Qiskit}, we sampled
$249$ one-qubit Pauli channels and simulated them using the ibmq-lima quantum
computer.  For each of these channels, we used quantum process
tomography~\cite{Qiskit, Chuang:1996} to obtain the 
operator $\xi_I$ corresponding to the implementation of the
circuit.  Then, we compared this {\color{red}
Choi matrix} {\color{orange} operator} with the theoretical {\color{red} Choi
matrix $\mathcal{C}_T$} {\color{orange} operator $\xi_T$} of the channel we
wanted to implement.  \cpnote{Quizá referirnos mejor al canal? Lo discutimos.}
\tbnote{Ah sí, mejor. Cambié lo que puse en rojo por lo que está en naranja.}

We shall use the diamond norm~\cite{Aharonov,Wilde}, which has a simple physical meaning related
with the probability that one can distinguish two channels \cpnote{Revisa esta 
frase a ver si te parece}.
% To perform this comparison, we used the diamond norm~\cite{Aharonov,Wilde},
% which gives us a method of discriminating \cpnote{no solo discrimina... todas
% las normas lo hacen, pero nos permite ver que tan parecidos son dos canales. 
% Es como la fidelidad. Itera.} between quantum channels \cpnote{Tambien esta frase
% no conecta bien con lo que sigue}.
In particular, suppose an agent is given one of the channels $\xi_I$, $\xi_T$
with probability $1/2$ each,
and tries to guess which channel they received
by applying it to a state $\rho$ and measuring the result.
Then, the maximal probability of success (out of all possible states $\rho$) that
the agent guesses correctly is~\cite{Benenti}:
\begin{equation}
\label{eq: probability-success}
p_{\succ} = \dfrac{1}{2}+ \dfrac{1}{4} ||\xi_I - \xi_T ||_{\diamond},
\end{equation}
where $|| \cdot ||_{\diamond}$ is the diamond norm \cpnote{no la hemos 
definido matemáticamente}.  
% Notice that $p_{\succ}=1/2$
% means that the channels are the same \cpnote{qioza una frase explicando porque
% esto es razonable}
% \tbnote{Cambiar la oración pasada por:} {\color{orange} 
Notice that if the channels are the same, then $p_{\succ}=1/2$. 
This is expected because in this situation the agent
has no way of distinguishing the channels and has no choice but to completely
guess, which results in a probability of success of $1/2$.
On the other hand, $p_{\succ}=1$ indicates that the channels are perfectly
distinguishable.
% \cpnote{hummm ejemplo al menos para nosotros.} 
% \tbnote{Un ejemplo que comprobé es considerar el canal que aplica $\sigma_x$ y 
% el que aplica $\sigma_z$ y tienen $p_{\succ}=1$.
% De hecho, al tomar dos canales que consistan en aplicar $\sigma_i$ y $\sigma_j$ 
% (para $i\neq j$), se cumple esto.
% También quería ejemplos no unitarios, pero no encontré.}

Finally, using the representation of Pauli channels in a tetrahedron as
in eq.~(\ref{eq: conditions-tetrahedron}),
we show in fig.~(\ref{fig: fidelity one qubit}) the maximal probabilities of
success defined by eq. (\ref{eq: probability-success}) for the channels
analyzed. 
We can see that channels close to the 
completely depolarizing
channel (that is close to the center of the tetrahedron)
have a low $p_{\succ}$, while those 
close to unitary channels have much higher $p_{\succ}$.
This means that channels closer to the 
completely depolarizing channel are simulated better on the quantum computers.
This is reasonable because quantum computers are prone to errors
that depolarize qubits, which isn't very problematic
when trying to simulate depolarization but it is 
when simulating unitary processes.
\cpnote{Siento qeu aun falta algo de análisis pero lo dejamos para cuando tengamos mas
figuras y mas inspiracion}

% \cpnote{Mejorar la figura, quizá dejando la tridimensional y ademas poniendo unos 6 cortes. Probar
% con diferentes colores.
% }

\begin{figure}[h!]
\centering
\includegraphics[width=0.45\textwidth]{probabilities-points.png}\\
\caption{{\bf Maximal probabilities of success for one-qubit Pauli channel}
$p_{\succ}$ of one-qubit Pauli channels implemented on IBM's ibmq-lima. The
channels are plotted in the tetrahedron of Pauli channels, with a color bar
indicating the distinguishability of each channel's implementation using the
circuit for a 1-qubit Pauli channel. \cpnote{Poner la barra del tamaño apropiado 
y quizá juntar con los cortes que tenemos. Discutir en vivo con Tomas a ver que onda. 
Tambien poner mas puntos experimentales.}}
\label{fig: fidelity one qubit}
\end{figure}

@@

@@

%\textbf{Puntos:}
%\begin{itemize}
%\item Use the last theorem to conclude directly which maps can be created using an OPR circuit.
%\item \textbf{Examples:} Show examples that satisfy these conditions: Bit-Flip, parabolic maps, etc. 
%and an example that doesn't satisfy the conditions (ejemplo está en la tesis).
%\end{itemize}
% }}}
\section{Exponential maps $e^{iHt}$} % {{{
\label{sec: Exponential maps}
\textbf{Puntos:}
